Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-23 conclusions.tex
Restructured second to last paragraph in conclusion
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1143 ccdd05d5-56c1-461a-bf98-85f6876523b4

Although we have demonstrated a feasible method for advance detection
\emph{filtering}, we have not yet explored data whitening, triggering,
coincidence, and ranking of gravitational wave candidates in a framework that
supports early \EM\ followup.
% I don't understand what is trying to be said here.  Time-slices have no
% cross-correlation with eachother since they are orthogonal.
\begin{comment}If adjacent time slices have non-negligible cross-correlation
with each other, then there may be some subtleties in the design of these
postprocessing stages that we must address in order to translate the
early-warning outputs into candidate events.\end{comment}
%
As one possible method of addressing the latter, the time-slice decomposition
and the \SVD\ will help us form low-latency signal-based vetoes (for example, a
$\chi^2$ statistic) that have been essential for glitch rejection used in
previous \GW{} \CBC{} searches.

>>>>

Although we have demonstrated a computationally feasible detection statistic for
advance detection, we have not yet explored data whitening, triggering,
coincidence, and ranking of gravitational wave candidates in a framework that
supports early \EM\ followup.  One complication in deploying a low-latency or
early-warning search is that whitening the detector data involves estimating the
noise power spectrum, which is often done in acausally.  We will have to look into
causal or low latency alternatives to conventional spectral estimation techniques.
Another potential complication is that if adjacent time slices have non-negligible
cross-correlation with each other, then there may be some subtleties in the design
of the triggering and coincidence stages that we must address in order to translate
the early-warning outputs into candidate events.  The time-slice decomposition and
the \SVD\ may also be beneficial for the postprocessing stage because they will
help us form low-latency signal-based vetoes (e.g. $\chi^2$ statistics)
that have been essential for glitch rejection used in previous \GW{} \CBC{}
searches.
